HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-17 paper/main.tex
minor
www

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}

@@

  \caption{\label{fig:ucca_example2}
    Sample UCCA annotation of a source sentence, translation (below in italics), 
    and translation judgements over the source units, marked with A,B,R,O,G labels. Yellow/blue marks
    nodes annotated with A/B, respectively.
    In our experiments, the translation is in German, Romaninan, Polish or Czech.
    ``became a passion'' is marked as atomic, as it is a multi-word expression.
    The dashed line indicates that ``she'' is also a child of the unit ``greatly improved''.
    UCCA categories, and alignment between source and translation are omitted for brevity.}

@@

Structural units have sub-units (children in the UCCA graph), which may either be
atomic or structural. The labels assigned to such nodes reflect the extent to which
the relation between the sub-units.
For instance, a Scene unit represents the relation between the
Scene elements, such as the predicate (main relation), participants and adverbials.
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong.
We make a three-way distinction between translation qualities with structural
nodes, as opposed to the two-way distinction with atomic units, as lexical units
often can have slight errors, in which cases we do want to provide partial credit.

There are many ways that the relationship between the children might go
wrong in translation:

@@

\XXX{Could someone review this for Ondrej.}
Note that for non-configurational languages, the relationship between the
governing and the dependent units is often expressed using morphological
properties of the dependents instead of their ordering (this holds especially for the verb and its
modifiers, less so for components of noun phrases). Since errors in morphology
should be expressed on the atomic units, we would expect
a higher proportion of ``Adequate'' structural units for Czech and Polish
compared to German and Romanian\oa{is this because that error would already be marked
  in the atomic units, and thus not in the structural ones?}.

We defined the labels to reflect adequacy,
rather than fluency judgements. Specifically, annotators are instructed to
label a unit as Adequate if its translation is understandable and preserves
the meaning of the source unit, even if its fluency is impaired.

@@

Another example is given in \figref{fig:ucca-tree-hume}.
%``Golf became an obsession for his oldest daughter, she took daily lessons and became very good'',
The figure shows an annotation of a UCCA tree, and an example annotation for
each of the units.
We see that ``became a passion'' is deemed atomic, as it is translated as a single unit
in $t$, and thus its sub-units, ``became'', ``a'' and ``passion'' are not evaluated
individually.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\listfiles

@@

  \caption{\label{fig:hume_tree}
    Sample UCCA annotation of a source sentence, translation (below in italics), 
    and translation judgements over the source units, marked with A,B,R,O,G labels. Yellow/blue marks
    nodes annotated with A/B, respectively.
    In our experiments, the translation is in German, Romaninan, Polish or Czech.
    ``became a passion'' is marked as atomic, as it is a multi-word expression.
    The dashed line indicates that ``she'' is also a child of the unit ``greatly improved''.
    UCCA categories, and alignment between source and translation are omitted for brevity.}

@@

Structural units have sub-units (children in the UCCA graph), which may themselves
either be atomic or structural. The labels assigned to such nodes reflect the extent to which
the relation between the sub-units is preserved in $t$.
For instance, a Scene unit represents the relation between the
Scene elements, such as the predicate (main relation), participants and adverbials.
Structural units are labeled as ``Adequate'' or ``Bad'', meaning
that the relation between the sub-units went wrong.
We use a three label system with atomic units, as
opposed to a two label one in structural units,
as lexical units often have slight errors, in which cases we do want to provide partial credit.

There are many ways that the relationship between the children might go
wrong in translation

@@

We note that HUME labels reflect adequacy, rather than fluency judgements.
Specifically, annotators are instructed to
label a unit as Adequate if its translation is understandable and preserves
the meaning of the source unit, even if its fluency is impaired.

In non-configurational languages, the relationship between the
governing and the dependent units is often expressed using morphological
properties of the dependents instead of their ordering
(this holds especially for the verb and its modifiers,
less so for components of noun phrases). Since errors in morphology
should be expressed on the atomic units, we would expect
a higher proportion of ``Adequate'' structural units for Czech and Polish
compared to German and Romanian\oa{but doesn't German also have a case system? Ondrej:
  could you pinpoint what the difference exactly is?}.

An example HUME annotation is given in \figref{fig:hume_tree},
which presents an annotation of a UCCA tree, and a corresponding translation.
We see that ``became a passion'' is deemed atomic, as it is translated as a single unit
in $t$, and thus its sub-units, ``became'', ``a'' and ``passion'' are not evaluated
individually.

@@
